### 2024-12-12 background.tex
Modified Background section, got problem with citing

The history of the Central Limit Theorem, hereinafter referred to as CLT, is quite a fascinating journey through the gradual development of probability theory. Over the years, various versions of CLT have been formulated, reflecting its adaptability and foundational importance. Each such variation addresses certain mathematical challenges and applications, therefore enriching the broader understanding of convergence in probability. In this chapter, we explore some theorem-proving tools and their methodologies to formalize the CLT, emphasizing ...

>>>>

The Central Limit Theory (CLT) is one of the main theoretical results from the  Probability theory, a bridge from individual randomness to aggregate predictability. It marks the gradual approach of mathematical rigor and upgrading of the theorem used by addressing more and more difficult problems. Over centuries, different forms of CLTs have been derived, each of which has added to its understanding convergence and applications. This chapter will present the historical development of the CLT that describes its milestones and contributions. It will also examine the modern theorem proving tools and ways of formalization, focusing on Lyapunov's approach.
